A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-07 paper.tex
Modify column title

\begin{table*}[h]
	\caption{Gas consumption for each function of Product Contract}
	\label{tab:gas}
	\centering
	\resizebox{0.7\textwidth}{!}{
	\begin{tabular}{|c|c|c|c|}
		\hline
		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
		\hline
		generate contract & Broker & 2251002 \\
		subscribe product & Consumer & 44486 \\
		upload signed key to consumer & Provider & 147369 \\
		upload certified key & Broker & 167678 \\
		update encrypt key & Provider & 166784 \\
		update the amount of uploaded data & Broker & 32825 \\
		request refund & Consumer & 22545 \\
		unsubscribe & Consumer & 22641 \\
		withdraw & Broker/Provider/Consumer & 14719 \\
		\hline
	\end{tabular}
	}
\end{table*}

>>>>

\begin{table*}[h]
	\caption{Gas consumption for each function of Product Contract}
	\label{tab:gas}
	\centering
	\resizebox{0.7\textwidth}{!}{
	\begin{tabular}{|c|c|c|c|}
		\hline
		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
		\hline
		generate contract & Broker & 2251002 \\
		subscribe product & Consumer & 44486 \\
		upload signed key to consumer & Provider & 147369 \\
		upload certified key & Broker & 167678 \\
		upload hased encryption key & Provider & 166784 \\
		update the amount of uploaded data & Broker & 32825 \\
		request refund & Consumer & 22545 \\
		unsubscribe & Consumer & 22641 \\
		withdraw & Broker/Provider/Consumer & 14719 \\
		\hline
	\end{tabular}
	}
\end{table*}
